---
title: "Project Proposal"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Working with data

Data source: <https://survey.keis.or.kr/eng/klosa/klosa01.jsp>

```{r data}
library(tidyverse)
library(haven)
library(dplyr)
library(foreign)
df <- read_dta("C:/Users/Catherine/Documents/한다은/For thesis/KLoSA_STATA_2022v1/new_str.dta")
df$rrr
```

We need 3 types of variables.

+-----------------------------------+-----------------------------------------------------------------+
| Type                              | Variables                                                       |
+===================================+=================================================================+
| Measures of happiness             | Life satisfaction (w08G030)                                     |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Depression (w08dep1)                                            |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | CESD-10 (w08sumcesd)                                            |
+-----------------------------------+-----------------------------------------------------------------+
| Social security system            | Application for Long-Term Care Insurance (long_ins)             |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Coverage by private health insurance (privat)                   |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | The number of enrolled annuity insurance products (w08F132,ann) |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Basic old-age pension income (w08senior_pension)                |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | National Health Insurance Registration (med_ins)                |
+-----------------------------------+-----------------------------------------------------------------+
| Socio-demographic characteristics | Gender(gender)                                                  |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Age (w08A002_age)                                               |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Marital status (marital)                                        |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Education (w08edu)                                              |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Frequency of meeting close people (w08A032)                     |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Region (w08region3)                                             |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Health status (w08C001)                                         |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Number of children (w08Ba003)                                   |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Income satisfaction (w08G027)                                   |
+-----------------------------------+-----------------------------------------------------------------+
|                                   | Employment (work)                                               |
+-----------------------------------+-----------------------------------------------------------------+



Let's make small data set with these variables:

```{r data}
data <- df %>% select(pid, gender, marital, w08A002_age, w08A032, w08region3, w08Ba003, w08G027, w08edu, w08C001, work,w08F132, med_ins, w08senior_pension, privat, long_ins, w08G030, w08dep1, w08sumcesd, w08mniw_y,  ann,w08C046, w08C301)

knitr::kable(summary(data))
```
```{r data_1}
```
## 2. Propensity Score Matching

```{r psm}
install.packages('moonBook')
library(moonBook)

mytable(w08mniw_y ~ w08dep1, data=data)
```
```{r}

data$dep <- ifelse(data$w08dep1 == 1, 1, 0)
data$tr <- ifelse(data$w08C046 == 1, 1, 0)
data$med_in <- ifelse(data$w08C301 == 1, 1, 0)
data$med_in <- ifelse((data$med_in == 1)&(data$w08mniw_y == 2018), 1, 0)
data$time <- ifelse(data$w08mniw_y >= 2018, 1, 0)
data$time <- as.factor(data$time)
data_2020 <- filter(data, w08mniw_y >= 2018)
model <- glm(med_in ~ gender + marital + w08A002_age + w08A032 + w08region3 + w08Ba003 + w08G027+ w08edu + w08C001 + work, family=binomial, data=data_2020)
summary(model)
```
```{r psm}
library(ggplot2)

score.table <- data.frame(ps=predict(model, type='response'),  med_in = model$model$med_in)

score.table %>% mutate(med_in = ifelse(med_in == 1, 'National Health Insurance', 'Medical Aid')) %>% ggplot(aes(x = ps, fill = med_in)) +  geom_histogram(color = 'white', position = 'dodge') +  theme_bw() + ylim(c(0,100)) +stat_bin(bins=30)
```
```{r psm}
library(MatchIt)
data_new <- data %>%  # MatchIt does not allow missing values
  select(dep,marital, w08A002_age, w08A032, w08region3, w08G027, w08edu, w08C001, work, med_ins,med_in, w08mniw_y, w08sumcesd, w08G030
         ) %>%
  na.omit()
match_fit <- matchit(med_in ~ marital + w08A002_age + w08A032 + w08G027+ w08edu + w08C001 + work, method='nearest', data=data_new)
matched_dat <- match.data(match_fit)
dta_m <- match.data(match_fit)
dim(dta_m)
table(matched_dat$dep)

write.dta(dta_m, "hurray.dta")
write_dta(dta_m, "hurray.dta")
```
## 3. Estimating treatment effects


```{r welch}
with(dta_m, t.test(med_in ~ dep))
```
```{r did_dep}
lm_treat1 <- lm(dep ~ med_in*w08mniw_y, data = dta_m)
summary(lm_treat1)

```
```{r did}
lm_treat2 <- lm(dep ~ med_in*w08mniw_y + marital + w08A002_age + w08A032 + w08region3 + w08G027+ w08edu + w08C001 + work, data = dta_m)
summary(lm_treat2)
```
```{r did_CESD10}
lm_treat3 <- lm(w08sumcesd ~ med_in*w08mniw_y, data = dta_m)
summary(lm_treat3)
```
```{r did_CESD10}
lm_treat4 <- lm(w08sumcesd ~ med_in*w08mniw_y + marital + w08A002_age + w08A032 + w08region3 + w08G027+ w08edu + w08C001 + work, data = dta_m)
summary(lm_treat4)
```
```{r did_life_exp}
lm_treat5 <- lm(w08G030 ~ med_in*w08mniw_y, data = dta_m)
summary(lm_treat5)
```
```{r did_life_exp}
lm_treat6 <- lm(w08G030 ~ med_in*w08mniw_y + marital + w08A002_age + w08A032 + w08region3 + w08G027+ w08edu + w08C001 + work, data = dta_m)
summary(lm_treat6)
```

## Other analyses
```{r d}
library(groom)
install.packages("data.table")

## Load data.table package
library(data.table)

all_models <- rbindlist(
    lm_treat2 %>% mutate(model = 1),
    lm_treat4 %>% mutate(model = 2),
    lm_treat6 %>% mutate(model = 3))

ols_table <- all_models %>%
    select(-statistic, -p.value) %>%
    mutate_each(funs(round(., 2)), -term) %>% 
    gather(key, value, estimate:std.error) %>%
    spread(model, value) 

```


```{r random}
install.packages('did')
library(did)

data$k <- ifelse(
                 ((data$w08mniw_y == 2020)& (data$med_ins == 0)), 2020,
                 ifelse(((data$w08mniw_y == 2018)& (data$med_ins == 0)), 2018,
                 ifelse(((data$w08mniw_y == 2016)& (data$med_ins == 0)), 2016,
                 ifelse(((data$w08mniw_y == 2014)& (data$med_ins == 0)), 2014,
                 ifelse(((data$w08mniw_y == 2012)& (data$med_ins == 0)), 2012,
                 ifelse(((data$w08mniw_y == 2010)& (data$med_ins == 0)), 2010,
                 ifelse(((data$w08mniw_y == 2008)& (data$med_ins == 0)), 2008,
                 ifelse(((data$w08mniw_y == 2006)& (data$med_ins == 0)), 2006, 0))))))))
data1 <- data %>%
   group_by(pid) %>%
   mutate(min_value = min(k)) %>% arrange() %>% head() 

head(data1)


is.numeric(data$min_value)  
data$e <- as.numeric(data$min_value)

data$rrr <- ifelse(data$rrr == 2006, 2008, 0) 

require(dplyr)

example_attgt <- att_gt(yname = "w08sumcesd",
                        tname = "w08mniw_y",
                        idname = "pid",
                        gname = "rrr",
                        data = df,  allow_unbalanced_panel = TRUE,
                        control_group = "notyettreated"
                        )

summary(example_attgt)
```
